Social Visual Analytics: DevOps for Data Scientists

### 2015-03-22 interviews.tex
organize based on feature/complaint grid

Raif: ``I've been sharing my notebooks in order for other people to see what I've done. It's very convenient for that purpose, I would say'' ``we haven't been editing them together, but we've been just sharing, and then I've been looking at these things that other people do. So there's no collaborative aspect of it, like developing the code, but there's like sharing aspects for other people to see and for me to see other people's notebooks'' ``the fact that we have all the notebooks there, searchable, it just saves me from replicating what other people have done'' ``there already is some person who has done something similar, and then you're able to just edit that, and that's saved a lot of work time for me''

@@

Clint: ``instead of looking back and saying I've got a billion files here in this subdirectory and I hope I've got them backed up, if they're on RCloud I know they are'' ``I don't have to worry about it if I drop my computer in the bathtub, everythings gone, because I'm not great about uploading my own for versioning, right?''

@@

\subsection{Web integration}
Horace ``that also means the other guys who want to do analytics on the data, they can first pull the data, do the analytics on it, and then feed the viewer the data. So if anyone from the stats group wants to insert some code in between the data pulling procedure - now it's just database to GUI, and you can always insert something in between. We were trying to make such an example so that they don't have to rewrite the GUI part and they know how to get the data source, once you get the data into RCloud, then you have a dataframe to work with, and then they know how to produce another dataframe. We give them the specification of the dataframes, we give them the data input, they do whatever they want, they can reuse the data connection part and the GUI part. We can keep changing these components and that's a very nice thing.''

@@

Raif: ``cells are really useful'' but ``whatever you type on the command line, it becomes a part of your notebook, and I find it a little bit annoying, because I really type a lot of things to check my data, and I don't want that to become a part of the notebook'' ``Like you're kind of checking out what your data is, or you make a plot of the data. Things that should not really become part of a notebook, but things that help you understand your data better.'' ``for example imagine I run a cell whose output is huge, right, and now that output would block the whole window, and in order to find the next cell, I have to scroll down, and find where that cell starts, right? So, I'm losing the continuity of my code to the output''

@@

\subsection{Long-running cells}
Kenny: Problem of long-running cells.  ``The long tail.''  First cell takes seconds to run, next cell minutes, next cell 5 hours.  In this scenario, which is common for Kenny, the ``Run whole notebook'' button is dangerous. This is also a huge issue for demoing code.  Suggests something like knitr's caching of results. When converting his work to notebooks, Kenny ends up with a lot of comments that say ``this cell takes a long time to run.'' He ends up ``littering the notebook with little switches that comment out'' the slow parts and ``load the object instead'', ``save the object to disk''.

@@

@@

\subsection{Version management difficulties}
Rick: ``I don't need something that keeps track of every mistake I've made or every direction I've tried.” ``namespaces are already crowded, so trying to remember the names of notebooks is hard, much less the names of states within each notebook.''

@@

@@

\subsection{Web snafus}
Disconnection, slowness

Corey: ``“What frustrates me is that if I do leave this window for what feels like 5 or 7 minutes, it disconnects and I have to reconnect and run the whole notebook again.''

\subsection{Other}
Byers: There is also a big problem with ``bitrot'' - notebooks often stop working because the user changed the structure of their data, changed a filename or a database.  We need ``organizational protocols'' to catch up with the technology.  There is a ``hysteresis between the technical and the social'' and we have not yet adapted.

>>>>

Raif: ``I've been sharing my notebooks in order for other people to see what I've done. It's very convenient for that purpose, I would say'' ``we haven't been editing them together, but we've been just sharing, and then I've been looking at these things that other people do. So there's no collaborative aspect of it, like developing the code, but there's like sharing aspects for other people to see and for me to see other people's notebooks'' ``there already is some person who has done something similar, and then you're able to just edit that, and that's saved a lot of work time for me''

@@

Clint: ``instead of looking back and saying I've got a billion files here in this subdirectory and I hope I've got them backed up, if they're on RCloud I know they are'' ``I don't have to worry about it if I drop my computer in the bathtub, everythings gone, because I'm not great about uploading my own for versioning''

@@

\subsection{Search}
Raif: ``the fact that we have all the notebooks there, searchable, it just saves me from replicating what other people have done'' ``One way of thinking of it is like Google Code, you know you just search for something and you find something useful and you just use it. It’s a repository of code''

Rick: ``And the same kind of thing when you search through notebooks, usually I know somebody’s notebooks that I want to search through, like I’ll search through Simon Urbanek’s first, then I’ll go off to somebody else’s, because I know that the kind of thing I’m looking for something more obscure than I’m likely to find in some random person’s thing''

\subsection{Web integration}
Horace ``that also means the other guys who want to do analytics on the data, they can first pull the data, do the analytics on it, and then feed the viewer the data. So if anyone from the stats group wants to insert some code in between the data pulling procedure, [they] can always insert something in between. We were trying to make such an example so that they don't have to rewrite the GUI part and they know how to get the data source, once you get the data into RCloud, then you have a dataframe to work with, and then they know how to produce another dataframe. We give them the specification of the dataframes, we give them the data input, they do whatever they want, they can reuse the data connection part and the GUI part. We can keep changing these components and that's a very nice thing.''

@@

Raif: ``whatever you type on the command line, it becomes a part of your notebook, and I find it a little bit annoying, because I really type a lot of things to check my data, and I don't want that to become a part of the notebook'' ``Like you're kind of checking out what your data is, or you make a plot of the data. Things that should not really become part of a notebook, but things that help you understand your data better.''

@@

@@

Raif: ``cells are really useful'' but ``you want to see your output in a different window, on a separate part of the window'' ``for example imagine I run a cell whose output is huge, right, and now that output would block the whole window, and in order to find the next cell, I have to scroll down, and find where that cell starts, right? So, I'm losing the continuity of my code to the output''

@@

Kenny: Problem of long-running cells.  ``The long tail.''  First cell takes seconds to run, next cell minutes, next cell 5 hours.  In this scenario, which is common for Kenny, the ``Run whole notebook'' button is dangerous. This is also a huge issue for demoing code.  Suggests something like knitr's caching of results. When converting his work to notebooks, Kenny ends up with a lot of comments that say ``this cell takes a long time to run.'' He ends up ``littering the notebook with little switches that comment out'' the slow parts and ``load the object instead'', ``save the object to disk''.

@@

\subsection{Versioning not useful}
Rick: ``I don't need something that keeps track of every mistake I've made or every direction I've tried.” ``namespaces are already crowded, so trying to remember the names of notebooks is hard, much less the names of states within each notebook.''

\subsection{Web snafus}
Corey: ``“What frustrates me is that if I do leave this window for what feels like 5 or 7 minutes, it disconnects and I have to reconnect and run the whole notebook again.''

@@

\subsection{Other observations}
Byers: There is also a big problem with ``bitrot'' - notebooks often stop working because the user changed the structure of their data, changed a filename or a database.  We need ``organizational protocols'' to catch up with the technology.  There is a ``hysteresis between the technical and the social'' and we have not yet adapted.
